### 2014-11-19 CV/cv.tex
Added Optimization to CV research interests, changed order
Added more activities to CV

    6195 Gossard                            \hfill phone: (314) 313-1281          \vspace{0mm}\\\vspace{0mm}%
    East Lansing, Michigan, 48823                          \hfill email: brianwgoldman@acm.org          %\vspace{0mm}%\\\vspace{0mm}%
    %__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Research\\Interests}
    Evolutionary Computation, Artificial Intelligence, Machine Learning

@@

    %__________________________________________________________________________________________________________________
    % Honors and Awards
    \section{\mysidestyle Honors and\\Activities}
    Best Paper - Genentic Algorithms Track for GECCO 2014 ``Parameter-less Population Pyramid''\\%
    Peer Reviewer, IEEE Transactions on Evolutionary Computation Journal 2014--present\\%
    Founder and organizer, Computational Evolution Discussion Group October 2013--present\\%
    Program Committee Member, GECCO 2012--present Genetic Algorithms Track \vspace{1mm}\\%
    Voted 2012 Leader of the Year, Missouri S\&T Computer Science Department \vspace{1mm}\\%
    %Chair of ACM SIG for AI competition game development (SIG-Game), 2011--2012 \vspace{1mm}\\%
    Google AI challenge, ranked 25$^{th}$ out of 4619 world wide, 6$^{th}$ in USA, 2010 \vspace{1mm}\\%
    Missouri S\&T Human versus Computer chess tournament, two first place AIs, 2009 and 2011 \vspace{1mm}\\%
\begin{comment}    
    ACM SIG-Game Competition testing and balancing using evolving AI, 2009--2012 \vspace{1mm}\\%
    ACM SIG-Game first place AI, 2008          \vspace{1mm}\\%
    University of Illinois at Urbana-Champaign MechMania AI competition second place AI, 2007  \vspace{1mm}\\%
    Missouri S\&T Alumni Scholarship 2006--2010             %\vspace{1mm}\\%

>>>>

    6195 Gossard                            \hfill phone: (314) 313-1281          \vspace{0mm}\\\vspace{0mm}%
    East Lansing, Michigan, 48823                          \hfill email: brianwgoldman@acm.org          %\vspace{0mm}%\\\vspace{0mm}%
    %__________________________________________________________________________________________________________________
    % Research Interests
    \section{\mysidestyle Research\\Interests}
    Optimization, Artificial Intelligence, Evolutionary Computation, Machine Learning

@@

    %__________________________________________________________________________________________________________________
    % Honors and Awards
    \section{\mysidestyle Honors and\\Activities}
    Best Paper - Genentic Algorithms Track for GECCO 2014 ``Parameter-less Population Pyramid''\\%
    Co-chair, GECCO 2015 Combinatorial Black Box Optimization Competition\\%
    Peer Reviewer, IEEE Transactions on Evolutionary Computation Journal 2014--present\\%
    Founder and organizer, Computational Evolution Discussion Group October 2013--present\\%
    Program Committee Member, GECCO 2012--present Genetic Algorithms Track \vspace{1mm}\\%
    Voted 2012 Leader of the Year, Missouri S\&T Computer Science Department \vspace{1mm}\\%
    Chair of ACM SIG for AI competition game development (SIG-Game), 2011--2012 \vspace{1mm}\\%
    Google AI challenge, ranked 25$^{th}$ out of 4619 world wide, 6$^{th}$ in USA, 2010 \vspace{1mm}\\%
    Missouri S\&T Human versus Computer chess tournament, two first place AIs, 2009 and 2011 \vspace{1mm}\\%
\begin{comment}    
    ACM SIG-Game Competition testing and balancing using evolving AI, 2009--2012 \vspace{1mm}\\%
    ACM SIG-Game first place AI, 2008          \vspace{1mm}\\%
    University of Illinois at Urbana-Champaign MechMania AI competition second place AI, 2007  \vspace{1mm}\\%
    Missouri S\&T Alumni Scholarship 2006--2010             %\vspace{1mm}\\%
